Tropical Andes plant trait data GIFT

### 2025-08-27 code/L0/L0_TropicalAndes_plants_GIFT.Rmd
Added name; code works fine but could probably add a function later

---
title: "Tropical Andes plant trait data GIFT"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script retrieves plant trait data from the GIFT database for plant species list."
data input: "none"
data output: "TropicalAndes_GIFT_plant_traits.csv"
date: "2023-08-03"
output: html_document
---

@@

```{r}
# 
height_mean <- GIFT_traits(trait_IDs = c("1.6.3"))
height_min <- GIFT_traits(trait_IDs = c("1.6.1"))
height_max <- GIFT_traits(trait_IDs = c("1.6.2"))

>>>>

---
title: "Tropical Andes plant trait data GIFT"
author: "Hazel J. Anderson, Jenna B. Baljunas"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script retrieves plant trait data from the GIFT database for plant species list."
data input: "none"
data output: "TropicalAndes_GIFT_plant_traits.csv"
date: "2023-08-03"
output: html_document
---

@@

```{r}
# maybe make into function later?
height_mean <- GIFT_traits(trait_IDs = c("1.6.3"))
height_min <- GIFT_traits(trait_IDs = c("1.6.1"))
height_max <- GIFT_traits(trait_IDs = c("1.6.2"))
